Effects of rotation on the Lyman-$\alpha$ line morphology in distant galaxies

### 2013-03-11 paper/Analisis.tex
minor change
Mejoras de algunas graficas
a little modification
plots Xm vs costheta
follow-up idea

In the following subsections we quantify the trends observed in
Fig. \ref{fig:differentvelocities} and
Fig. \ref{fig:differentobservers} as a function of the maximum
rotation velocity $V_{\rm max}$ and the position of the observer with
respect to the rotation angle, $\mu = \cos{\theta}$. All the results
in this section will be expressed in terms of frequencies expressed in
velocities.

@@

>>>>

In the following subsections we quantify the trends observed in
Fig. \ref{fig:differentvelocities} and
Fig. \ref{fig:differentobservers} as a function of the maximum
rotation velocity $V_{\rm max}$ and the position of the observer with
respect to the rotation angle, $\mu = \cos{\theta}$. All the results
in this section will be expressed in terms of resframe wavelength.

@@

%ideas:
Keep in mind making a follow up paper on the results of Yamada et atl http://adsabs.harvard.edu/abs/2012ApJ...751...29Y on the line morphology at z=3.1. How many of these laes can be considered to have rotation features? In principle, all of then should have them. How to make the case convincing in the statistical sense?
